%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Mckinsey \& Company}{Feb 2023 -- Now}
    {Software Engineer}{HCMC, Vietnam}
    \resumeItemListStart

        \resumeItem{Foundation engineer of the \textbf{PropTech platform}, responsible for feature implementation, giving technical insights to the SA and driving the team in making techstack decision during the initial state. Successfully launched the first end-to-end online house buying journey in the Middle East, gaining more than \textbf{SAR 3.2B revenue} after 1 year.}
                % With the use of latest technologies \textbf{ReactJS, React Native, Spring Boot, GCP, Postgres, Redis, GCP PubSub, Strapi, ELK, Google Analytics..}.

        \resumeItem{\textbf{Lead the DevOps \& Backend workstream} for a client study to \textbf{manage \& analysis human resources for a government}. Responsible for deploying, managing and increasing scalability of the software for on-prem servers. Significantly reduce deployment time, application reliability \& time to market with the use of technologies \textbf{FastAPI, ReactJS, RHEL, MSSQL,...}}
        
        \resumeItem{Collaborated with the senior colleagues in maintenance and feature implementation for an \textbf{Online Sites Scanning platform} using \textbf{ReactJS, NodeJS, AWS Cloud, Terraform}. This was used across Client Service Teams, client's eCommerce sites and uplift \textbf{20\% profit per year} after integration.}
        
        \resumeItem {Collaborated with colleagues in an internal project to build a \textbf{Golang Auth Server} that serves for \textbf{multi-tenants}. This removes the redundancy and avoid internal teams to re-invent the wheel by introducing a finest Auth server.}


    \resumeItemListEnd
    
    \resumeSubheading
    {TVT Group}{Jul 2021 -- Jan 2023}
    {Software Engineer}{HCMC, Vietnam}
    \resumeItemListStart        
        \resumeItem{Core engineer in the \textbf{F\&B POS application} building team. Gathered client's requirements, designed, implemented and driving knowledge transfer sessions to the client team. The product then is served for the top 5 coffee brand in Vietnam, with \textbf{more than 500 stores} and \textbf{more than 50K customers} per day.}
        
        \resumeItem{Collaborated closely to seniors, owned core workstreams and remote delivered mobile application to client in \textbf{Health Industry} using \textbf{Android Native, Firebase, Realtime chat, Google Pay, Admob, Maps, Play Store,...} This was the first interactive AI Therapist in Japan and \textbf{reached 10K+ download} in the first public released version.}

        \resumeItem{Foundation engineer in a \textbf{PropTech platform}, main contact point of many workstream, including \textbf{booking appointment, appraising property, notification, real time chat}... The product then raised and funded up to \$1M.}
    \resumeItemListEnd

    \resumeSubheading
    {Resumind}{May 2021 -- Jan 2022}
    {Software Engineer, Contract}{HCMC, Vietnam}
    \resumeItemListStart
        \resumeItem{\textbf{Upholds the startup value by 30\%} with the implementation of an \textbf{end-to-end production-ready learning platform}.}
        \resumeItem{Frequently \textbf{hosted knowledge transfer sessions} to the team in multiple domain including \textbf{Backend (FastAPI), Mobile(Flutter), Infrastructure Provisioning (AWS)}}
    \resumeItemListEnd

\resumeSubHeadingListEnd